TacticToe: Learning the Game of Tactics

### 2018-01-24 tactictoe_jv.tex
scaling distribution

\begin{figure}[h]
\centering           
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=3000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}     
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{scaled \tactictoe,original}
\end{axis}
\end{tikzpicture}
\caption{Number of original proofs with a number $x$ of tactic units. 
         Since there is about two-third of the original proofs that have a 
         respective \tactictoe proofs, we scale the number of 
         \tactictoe proofs by a factor of $\frac{1}{0.662}$.. 
\tactictoe 
 proofs.}
\end{figure}

>>>>

\begin{figure}[h]
\centering           
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=3000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}     
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{\tactictoe proofs,original proofs}
\end{axis}
\end{tikzpicture}
\caption{Number of original and \tactictoe proofs with a number $x$ of tactic 
units. For comparing of the distribution, the number of \tactictoe proofs was 
scaled by the inverse of \tactictoe's success rate $\frac{1}{0.662}$.}
\end{figure}

There are more in proportion \tactictoe small proofs than original human proofs.
